\documentclass[10pt,draftclsnofoot,onecolumn]{article}
\usepackage{a4wide}

\renewcommand{\baselinestretch}{1.5}

\usepackage{amsthm}
\usepackage{amsfonts,amssymb}
\usepackage{amsmath} % Required for some math elements

\usepackage[linesnumbered,vlined,ruled]{algorithm2e}
\usepackage{graphicx}
\usepackage{subfigure}

\usepackage{cite}
%\usepackage{hyperref}
%\usepackage[numbers,sort&compress]{natbib}

\usepackage{xcolor}
%\usepackage[usenames,dvipsnames]{color}
%\usepackage{mathrsfs}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{rotating}

\usepackage{amsfonts,amssymb}

%\usepackage{ulem}
%\usepackage{cancel}

\usepackage{diagbox}
\usepackage{sgame}
%\usepackage{ulem}
%\usepackage{sgamevar}
%\usepackage{egameps}
%\usepackage{caption2}

\usepackage{caption}
\usepackage{sidecap}
\usepackage{url}

%\usepackage{tablefootnote}
\usepackage{booktabs}
\usepackage{threeparttable}

\usepackage{array}
\newcommand{\tann}[1]{\textcolor{black}{#1}}

\newcommand{\fixit}[1]{{\leavevmode\color{red}#1}}

\begin{document}

Dear Editor,

We are pleased to submit our paper titled ``Distributed Job Dispatching in Edge Computing Networks with Random Transmission Latency: A Low-Complexity POMDP Approach" for possible publication in IEEE Internet of Things Journal.
% IEEE Transactions on Mobile Computing.

A preliminary version with part of the results appeared in IEEE MSN 2020, which won the Best Track Paper Award in ``Algorithms, Theory, and Protocols Track". Compared with the conference publication, the current submission makes the following novel contributions:

\begin{enumerate}
\item \textbf{New or Improved Algorithm: }
\begin{itemize}
    \item In the conference paper, we proposed a novel low-complexity approximate MDP solution framework with known statistics in the system.
    In this manuscript, we add a section of ``Reinforcement Learning Algorithm'' to extend our framework with an efficient reinforcement learning approach to handle the situation when the priori knowledge of the system randomness is unknown. [Please refer to Section VI]
    \item In this submission, we revise the equations of the approximated value functions to avoid unnecessary calculations in distributed policy update in Problem 3, \tann{which further alleviates the computational complexity of value function evaluation.} [Please refer to Lemma 3 in Section V.B]
\end{itemize}

\item \textbf{New Theory:}
In the conference paper, we only gave a loose performance lower bound for the proposed distributed dispatching policy. In this paper, we provide a tighter semi-analytical performance lower bound \tann{based on an intermediate policy} [Please refer to Lemma 4 in Section V.C]. Furthermore, we prove that \tann{the performance gap between the intermediate policy and our propose policy} would monotonically decrease with respect to a parameter $T$ [Please refer to Appendix D].
% tighter bound \tann{of the problem P1 to minimize the discounted sum of the cost} and our proposed policy would monotonically decrease with respect to a parameter $T$.

\item \textbf{More Comprehensive Simulations:}
In this submission, we add two numerical simulations to demonstrate the monotonic performance gap decreasing and the convergence of reinforcement learning algorithm, respectively. \tann{The simulation results demonstrate the performance of the reinforcement learning algorithm and the tighter performance lower bound, respectively, which are well in line with the expectations.} [Please refer to Fig. 7 and Fig. 8 in Section VII]
% {we add a new sensitivity experiment showing the percentage of local detection used with higher arrival rate.

\item \textbf{More Details:}
In the conference paper, due to the limited space, we did not elaborate completely the proofs of quite a few important lemmas and theorems, e.g., the analytical performance lower bound.
% the analytical expression of approximate value functions on APs and edge servers,
In this submission, we complete all the proofs in the appendices of the lemmas with fulfilling details. [Please refer to the Appendix A, B and C]


% % \item In the INFOCOM paper, we only solve the HetNets uplink scheduling problem using our  proposed algorithms. However, our solution framework can be applied to  a series of scheduling problems in multi-tier networks. In this submission, we add a section that extensively discusses how to extend our solution to other important multi-tier networks including Cloud-RAN and Mobile Edge Computing. [Please refer to Section 5]
% \item In this manuscript, we add a section of ``Background and Motivation'' to justify the setting of the limited backhaul capacity, and the motivation why we adopt reinforcement learning due to the diversity and time-varying characteristics in HetNets. [Please refer to Section 2]}
% \item In the INFOCOM paper, {we adopt discounted accumulated cost over infinite time-horizon when modelling the HetNets uplink scheduling problem. In this manuscript, we model the problem with a more realistic cost function, i.e., the average cost over infinite time-horizon, which is naturally derived from the real scenario [Please refer to Problem 1]. Our proposed algorithm has two approaches for the average cost model and the discounted cost model, respectively. For the average cost model, we add a new Bellman equation [Eqn. (9)], new reference states [Eqn. (14)], and a new $\mathbb Q$-function updating rule [Eqn. (18)]. Moreover, we bridge the gap between the average cost model and the discounted cost model by providing a justification of the benefits of discounted cost model. [Please refer to Section 4.1]}
% \item In the INFOCOM paper, {we assume the joint detection is a binary decision, i.e., each frame's signal can only be either jointly detected or local detected. In this submission, we improve this decision by allowing a portion of sub-frames to be locally detected. We further consider the case that the pico-BS may have limited detection ability that can only detect a limited number of sub-frames. [Please refer to Section 3.2]}
% add an evaluation here?
% \item In the INFOCOM paper, {we only give the end-to-end delay as the cost function. Actually, the cost function can be general to  cover other forms of cost. In this submission, we propose two other forms of cost functions: the throughput and the power consumption. We also explain why using the end-to-end delay as cost function already maximizes the throughput. [Please refer to Remark 1 in Section 3.4]}
% \item In the INFOCOM paper, {we did not elaborate the related works in details. In this submission, we extensively introduce the related works, and compare them with our work. [Please refer to Section 2]}
% \item In this submission, {we add a new sensitivity experiment showing the percentage of local detection used with higher arrival rate. [Please refer to Fig. 6]}
% \item In the INFOCOM paper, {the proofs of NP-hardness, the data rate derivation, the convergence and the error bound are omitted due to limited space. We complete all the proofs in the appendices in this submitted manuscript. [Please refer to the Appendix A, B, C and D]}
% %\item \tant{In the INFOCOM paper, we only investigated the HetNets uplink scheduling problem. Actually, our solution framework can be applied to  a series of scheduling problems in multi-tier networks. In this submission, we add a section that extensively discusses how to extend our solution to other important multi-tier networks including Cloud-RAN and Mobile Edge Computing. [Please refer to Section 5]}
\end{enumerate}

Based on the aforementioned extensions, we believe this submitted manuscript comprises a significant technical contribution compared with the previous conference version.\\

Thank you very much and we look forward to your feedbacks on this submission.\\

Best Regards,

Yuncong Hong
\vspace{+20mm}

\noindent [1] Y. Hong, B. Lv, R. Wang, H. Tan, Z. Han, H. Zhou, F. C. M. Lau, ``Online Distributed Job Dispatching with Outdated and Partially-Observable Information'', in Proc. \emph{IEEE MSN}, 2020 \textbf{Best Track Paper Award}.\\
% \noindent [1] Z. Han, H. Tan, R. Wang, S. Tang and F. C. M. Lau, ``Online Learning based Uplink Scheduling in HetNets with Limited Backhaul Capacity'', in Proc. \emph{IEEE INFOCOM}, 2018\\
\end{document}